
\subsection*{Potential Risks}
In order to prevent unexpected setbacks in the development of the product, a set of possible risks has been considered:
\begin{itemize}
    \item The PC used for developing the audio system breaks.
    \begin{itemize}
        \item Use a cloud storage method for both code base and documentation, such as GitHub, to prevent any data loss.
        \item Do not leave the PC unsupervised in public areas.
    \end{itemize}
    \item The FPGA kit breaks, and development is stalled.
    \begin{itemize}
        \item Avoid unnecessary transportation of the kit.
        \item Only use the kit in a trusted and safe environment.
        \item Use simulation testbenches as the main method of verification. Only perform hardware testing after simulations are denoted as successful.
    \end{itemize}
    \item Student is ill or unable to work.
    \begin{itemize}
        \item Respect a healthy schedule and maintain an adequate balance of rest and time dedicated to work.
        \item Consider ergonomic recommendations, such as correct posture or appropriate room lighting.
        \item Divide project objectives into mandatory and optional categories to allow deprioritisation of goals in the case of an unfortunate event.
    \end{itemize}
\end{itemize}


\subsection*{Resources}
\begin{itemize}
    \item The system will be created in the SystemVerilog language. Code will be developed using Visual Studio Code and Xilinx Vivado. The latter will also be used for simulations and testbench creation.
    \item The developed code and documentation will be synchronised with an online GitHub repository.
    \item The FPGA board that will be used is a \textit{Xilinx Zybo Z7-20}.
    \item The music equipment used is:
    \begin{itemize}
        \item Harley Benton JB-20 Bass Guitar
        \item Fender Rumble 40 Amplifier
        \item 6.35mm Jack cables and 6.35mm Jack to 3.5mm Jack adapters 
    \end{itemize}
\end{itemize}


